Project-I by Group MexicoCity

### 2014-11-02 report/paper.tex
report update - skeletton ------------------------ no time to continue before 17h comments.rtf will be used

\end{itemize}

\section{Summary}
In this report, we analyzed a regression dataset and found that ridge regression is a reasonable fit. We estimate that the average test error is 1.213 ($\pm$ 0.02). We tried some feature transformation and found that there is a small improvement giving us a test error of around 1.198 ($\pm$ 0.015). This improvement, however, is not significant.

>>>>

\end{itemize}
These functions are different machine learning methods.

\textcolor{red}{Formula? Not even sure this section is useful}

\section{Data observation}
We have two data set. One for regression and one for classification. \begin{description}
\item[Regression] Consists of output variables $\mathbf{y}$ and input variables $\mathbf{X}$. The number of example is $N = 1400$ and each input $\mathbf{x_n}$ has dimensionality $D = 48$. The first $34$ are real valued and the last $14$ are categorical.
\item[Classification]

\end{description}

\section{Data visualization and cleaning}
\textcolor{red}{Histogram, correlation, applied methods}

\section{Best method : Ridge Regression}
\textcolor{red}{explain what is the best method and why for our dataset, add some figures and results}
\section{Feature transformations}
\textcolor{red}{Different transformation (myPoly, sqrt, etc)}
\section{Summary}
\textcolor{red}{summarize in a few lines and write down all the final results}
